### 2015-07-08 narrative/proposed-work.tex
Reworked new paragraph in proposed research section

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layer} needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often mean that science is not performed well.

>>>>

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layer} needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often means that science is not performed well.

We aim to alleviate the need for the ``magic'' and ``tricks''
that are currently required to optimize application I/O performance
on today's file systems. To accomplish this, we will provide a systematic
approach for describing intentions and other knowledge from {\it user}
space, as well as hidden knowledge of the underlying storage layers.
%For example, ADIOS contains most of the ``best practices'' for I/O optimizations for
%   each file system, and as users place more knowledge into ADIOS, ADIOS
%   can make optimizations.
By capturing user intentions and acting upon them in the middleware, we
free the user from polluting application code with system specific
optimizations which may provide better performance in the short term,
but are detrimental to the long-term maintainability of applications, and
are more sensitive to changes to system configuration. We have successfully
employed this strategy of separation of concerns in ADIOS, and believe that
it will become increasingly important as users want to describe more about
the storage hierarchy and the priorities of different chunks of data. 
Our research is aimed to allow users to simply describe these things and
utilize the descriptions so that the best optimizations can be made.
